FraCaS: 80 percent complete

### 2019-02-20 paper2018/paper.tex
background part added

\section{Introduction}
Natural Language Inference (NLI) is task of determining of whether an NL hypothesis H follows from an NL premise(s) P. NLI has received a lot of attention in the Computational Semantics literature and has been approached using a variety of techniques, ranging from logical approaches  \citet{bos:2008,Mineshima:2015,Abzianidze:2015,bernardy_type_2017} all the way to the recent Deep Learning (DL) models for NLP. The latter approaches, following the general trend in NLP, have been dominating NLI and indeed a number of impressive results have been produced. State-of-the-art DL systems achieve an accuracy of around 0.9 when tested on suitable datasets. However, the datasets that are used are assuming a definition of inference that can be thought to be looser compared to the definition assumed in platforms that used to test logical approaches. Consider the following two examples, one from the SNLI dataset, predominatly used to test DL approaches, and the FraCaS test suite, the dataset \textit{par excellence} to test logical approaches.

@@

In the SNLI case, one has to make a number of non-trivial assumptions in order to arrive at a contradiction:  a)  the two situations described have to be taken to refer to  the same situation and, thus, decide  whether one description contradicts the other, b) the indefinite article in the premise has to be identified with the indefinite article in the hypothesis, i.e.  \textit{man} contradicting \textit{woman} (a person cannot be a man and a woman at the same time). This is part of the reasoning humans perform, but it is not the only one. More precise, logical reasoning can be also performed. Such an example is the FraCaS example, as well as very fine-grained cases like the Antecedent Contained Deletion  ellipsis example below:

@@

For this reason, and despite the dominance of DL approaches in pretty much all NLP tasks, logical approaches have been continuing to be developed and evaluated on datasets like the FraCaS test suite and the SICK dataset \cite{marelli:2014}.  \citet{bernardy:2017}  define  a correspondence between abstract syntax parse trees of the FraCas examples, parsed using the Grammatical Framework (GF, \citet{Ranta:GF}), and modern type-theoretic semantics that are output in the Coq proof assistant (the FraCoq system).  The accuracy is 0.85 for 5 ections of the FraCaS test suite. The \textsc{Langpro} system presented by \citet{abzianidze:2017} is based on a Natural Logic tableau theorem prover. It achieves an accuracy of .82 on the SICK dataset.

@@

\end{itemize}
\section{Background}

>>>>

\section{Introduction}
Natural Language Inference (NLI) is the task of determining of whether an NL hypothesis H follows from an NL premise(s) P. NLI has received a lot of attention in the Computational Semantics literature and has been approached using a variety of techniques, ranging from logical approaches  \citet{bos:2008,Mineshima:2015,Abzianidze:2015,bernardy_type_2017} all the way to the recent Deep Learning (DL) models for NLI. The latter approaches, following the general trend in NLP, have been dominating NLI and indeed a number of impressive results have been produced \citet{kim:2018,radford:2018,liu:2019}.\footnote{These are the three systems with the best results on SNLI in increasing order.} State-of-the-art DL systems achieve an accuracy of around 0.9 when tested on suitable datasets. However, the datasets that are used are assuming a definition of inference that can be thought to be `looser' or less precise compared to the definition assumed in platforms that used to test logical approaches. Consider the following two examples, one from the SNLI dataset, predominatly used to test DL approaches and which has a state-of-the-art performace of 0.911 \citet{lui:2019'}, and the FraCaS test suite, the dataset \textit{par excellence} to test logical approaches.

@@

In the SNLI example, one has to make a number of non-trivial assumptions in order to arrive at a contradiction:  a)  the two situations described have to be taken to refer to  the same situation and, thus, decide  whether one description contradicts the other, b) the indefinite article in the premise has to be identified with the indefinite article in the hypothesis, i.e.  \textit{man} contradicting \textit{woman} (a person cannot be a man and a woman at the same time). This is part of the reasoning humans perform, but it is not the only one. More precise, logical reasoning can be also performed. Such an example is the FraCaS example, as well as very fine-grained cases like the Antecedent Contained Deletion  ellipsis example below:

@@

For this reason, and despite the dominance of DL approaches in pretty much all NLP tasks, logical approaches have been continuing to be developed and evaluated on datasets like the FraCaS test suite and the SICK dataset \cite{marelli:2014}.  \citet{bernardy:2017}  define  a correspondence between abstract syntax parse trees of the FraCas examples, parsed using the Grammatical Framework (GF, \citet{Ranta:GF}), and modern type-theoretic semantics that are output in the Coq proof assistant (the FraCoq system).  The accuracy is 0.85 for 5 sections of the FraCaS test suite. The \textsc{Langpro} system presented by \citet{abzianidze:2017} is based on a Natural Logic tableau theorem prover. It achieves an accuracy of .82 on the SICK dataset.

@@

\end{itemize}
\section{Background: GF, Monadic Dynamic Semantics, Coq}

\section{GF}

\subsection{GF}
In GF, abstract syntax is comprised of: a) a number of syntactic
categories, and b) a number of syntactic construction functions. The latter
provide the means to compose basic syntactic categories into more complex
ones.  For example, consider the constructor: $AdjCN : AP → CN → CN$. This  expresses
that one can append an adjectival phrase to a common noun and obtain
a new common noun. Furthermore,  GF is equipped  with a library of mappings from abstract
syntax to the concrete s usyntax of varionatural languages. These mappings can be inverted by GF, thus offering
parsing from natural text into abstract syntax. However, in this project we skip the
parsing phase and use the parse trees constructed by \citet{Ljunglof:2012},
thereby avoiding any syntactic ambiguity. \textbf{Do you want to further comment here?}

\subsection{Coq}
Coq is an  interactive theorem prover (proof assistant)  based on the calculus of inductive
constructions (CiC), i.e.  a lambda calculus with dependent
types. Coq is arguably one of the leading proof assistants. It has
famously been instrumental in formalising a proof of the four-color
theorem \citep{Gonthier:2008}, a proof of the odd order theorem \citep{Gonthier:2013}, as well as developing CompCert, a formally verified compiler for C \citep{Leroy}. Coq is a very powerful reasoning engine that makes it fit for the task of NLI, when the latter is formalized as theorem proving task. Its underlying higher order logic is furthermore very expressive to express fine-grained logical semantics. Furthermore, Coq supports a number of constructions that we will be using notably dependent typing and subtyping. These features are used in order to take care of specific NL phenomena (e.g. subtyping is used in defining different adjectival inference classes).

\subsection{Dynamic Monadic Semantics}
